### 2014-06-11 ApTranscriptome_TR.Rmd
Cleaning up file

# Load Bioconductor libraries
#source("http://bioconductor.org/biocLite.R")
#biocLite("topGO")
#biocLite("Rgraphviz")
#biocLite("RDAVIDWebService")
#biocLite("GOSemSim")
library(topGO) 
library(Rgraphviz)

library(GOSemSim)

@@

# set "trt" to true values - truncated in file names for convenience

A22.TPM[val==3,val:=3.5]
A22.TPM[val==10,val:=10.5]
A22.TPM[val==17,val:=17.5]
A22.TPM[val==24,val:=24.5]
A22.TPM[val==31,val:=31.5]
A22.TPM[val==38,val:=38.5]
str(A22.TPM)

>>>>

# Load Bioconductor libraries
#source("http://bioconductor.org/biocLite.R")
#biocLite("topGO")
#biocLite("Rgraphviz")
#biocLite("RDAVIDWebService")
#biocLite("GOSemSim")
library(topGO) 
library(Rgraphviz)	
library(GOSemSim)

@@

# set "trt" to true values - truncated in file names for convenience
A22.TPM[val==3,val:=3.5]
A22.TPM[val==10,val:=10.5]
A22.TPM[val==17,val:=17.5]
A22.TPM[val==24,val:=24.5]
A22.TPM[val==31,val:=31.5]
A22.TPM[val==38,val:=38.5]
str(A22.TPM)
